Visualizing predictions

### 2021-02-28 effects_writeup.Rnw
Added methods for easy extension

<<set_up, echo=FALSE>>=
library(ggplot2)
library(margins)
library(effects)
library(emmeans)
library(jdeffects); jdtheme()

@@

<<echo=FALSE>>=
class(simple_pred_all) <- c("jdeffects", "data.frame") # plot.effects
simple_pred_all_plot <- (plot(simple_pred_all) 
	+ facet_wrap(~method) 
	+ theme(legend.position="bottom")
)
@

@@

<<echo=FALSE>>=
class(simple_pred_spec) <- c("jdeffects", "data.frame") # plot.effects
simple_pred_spec_plot <- (plot(simple_pred_spec)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
@

@@

<<echo=FALSE>>=
class(simple_pred_cat) <- c("jdeffects", "data.frame") # plot.effects
simple_pred_cat_plot <- (plot(simple_pred_cat)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
@

@@

The \pkg{zero\_vcov} function in \pkg{jdeffects} \emph{zeros-out} variance-covariances of non-focal terms of the predictor in question. For example:

@@

<<echo=FALSE>>=
class(simple_pred_all) <- c("jdeffects", "data.frame")
simple_pred_all_plot_out <- (plot(simple_pred_all)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
@

@@

<<label=simple_pred_spec_plot1, fig=TRUE, echo=FALSE, prefix=FALSE, include=FALSE>>=
class(simple_pred_spec1) <- c("jdeffects", "data.frame")
simple_pred_spec_plot1 <- (plot(simple_pred_spec1)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
simple_pred_spec_plot1
@

<<label=simple_pred_spec_plot2, fig=TRUE, echo=FALSE, prefix=FALSE, include=FALSE>>=
class(simple_pred_spec2) <- c("jdeffects", "data.frame")
simple_pred_spec_plot2 <- (plot(simple_pred_spec2)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
simple_pred_spec_plot2
@

@@

<<echo=FALSE>>=
class(simple_margpred_cat) <- c("jdeffects", "data.frame")
simple_margpred_cat_plot <- (plot(simple_margpred_cat)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
@

@@

<<echo=FALSE>>=
class(contr_pred_all) <- c("jdeffects", "data.frame")
contr_pred_all_plot_out <- (plot(contr_pred_all)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
@

@@

<<echo=FALSE>>=
class(contr_vcov_pred_all) <- c("jdeffects", "data.frame")
contr_pred_zeroed_vcov_plot <- (plot(contr_vcov_pred_all)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
@

@@

<<echo=FALSE>>=
class(contr_mmat_pred_all) <- c("jdeffects", "data.frame")
contr_pred_zeroed_mmat_plot <- (plot(contr_mmat_pred_all)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
@

>>>>

<<set_up, echo=FALSE>>=
library(ggplot2)
library(margins)
library(effects)
library(emmeans)
library(vareffects); varefftheme()

@@

<<echo=FALSE>>=
class(simple_pred_all) <- c("vareffects", "data.frame") # plot.effects
simple_pred_all_plot <- (plot(simple_pred_all) 
	+ facet_wrap(~method) 
	+ theme(legend.position="bottom")
)
@

@@

<<echo=FALSE>>=
class(simple_pred_spec) <- c("vareffects", "data.frame") # plot.effects
simple_pred_spec_plot <- (plot(simple_pred_spec)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
@

@@

<<echo=FALSE>>=
class(simple_pred_cat) <- c("vareffects", "data.frame") # plot.effects
simple_pred_cat_plot <- (plot(simple_pred_cat)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
@

@@

The \pkg{zero\_vcov} function in \pkg{vareffects} \emph{zeros-out} variance-covariances of non-focal terms of the predictor in question. For example:

@@

<<echo=FALSE>>=
class(simple_pred_all) <- c("vareffects", "data.frame")
simple_pred_all_plot_out <- (plot(simple_pred_all)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
@

@@

<<label=simple_pred_spec_plot1, fig=TRUE, echo=FALSE, prefix=FALSE, include=FALSE>>=
class(simple_pred_spec1) <- c("vareffects", "data.frame")
simple_pred_spec_plot1 <- (plot(simple_pred_spec1)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
simple_pred_spec_plot1
@

<<label=simple_pred_spec_plot2, fig=TRUE, echo=FALSE, prefix=FALSE, include=FALSE>>=
class(simple_pred_spec2) <- c("vareffects", "data.frame")
simple_pred_spec_plot2 <- (plot(simple_pred_spec2)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
simple_pred_spec_plot2
@

@@

<<echo=FALSE>>=
class(simple_margpred_cat) <- c("vareffects", "data.frame")
simple_margpred_cat_plot <- (plot(simple_margpred_cat)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
@

@@

<<echo=FALSE>>=
class(contr_pred_all) <- c("vareffects", "data.frame")
contr_pred_all_plot_out <- (plot(contr_pred_all)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
@

@@

<<echo=FALSE>>=
class(contr_vcov_pred_all) <- c("vareffects", "data.frame")
contr_pred_zeroed_vcov_plot <- (plot(contr_vcov_pred_all)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
@

@@

<<echo=FALSE>>=
class(contr_mmat_pred_all) <- c("vareffects", "data.frame")
contr_pred_zeroed_mmat_plot <- (plot(contr_mmat_pred_all)
	+ facet_wrap(~method)
	+ theme(legend.position="bottom")
)
@
